%+++ title = ``Credits'' author = ``The Embroidermodder Team'' date =
%``2022-09-19'' layout = ``default'' +++

\hypertarget{credits-for-embroidermodder-2-libembroidery-and-all-other-related-code}{%
\section{Credits for Embroidermodder 2, libembroidery and all other
related
code}\label{credits-for-embroidermodder-2-libembroidery-and-all-other-related-code}}

Please note that this file in not in alphabetical order. If you have
contributed and wish to be added to this list, create a new credit
bullet. Fill it in with your information and submit it to us. Supply
your: your full name or pseudonym and GitHub handle, if available.

Kinds of contribution:

\begin{itemize}
%\tightlist
\item
  Documentation - for changes to README files, manuals or help files.
\item
  Artwork - for artwork other than designs.
\item
  Bug Fixes - for small patches of a few lines.
\item
  Translation - for large patches to the translation files.
\item
  Designs - for an embroidery design sample or parametrized design as a
  toml file.
\item
  Bindings - for programming language bindings for libembroidery.
\item
  Commands - for Embroidermodder 2's in-built terminal.
\end{itemize}

finally there's ``Core Developer'' which is reserved for long term
contributors.

\hypertarget{contributors}{%
\subsection{Contributors}\label{contributors}}

\begin{itemize}
%\tightlist
\item
  Jonathan Greig (GitHub \texttt{redteam316}): Core Developer, Artwork,
  Documentation, Designs, Commands
\item
  Josh Varga (GitHub \texttt{JoshVarga}): Core Developer
\item
  Jens Diemer (GitHub \texttt{jedie}): Documentation
\item
  Kim Howard (GitHub \texttt{turbokim}): BugFixes
\item
  Martin Schneider (GitHub \texttt{craftoid}): Documentation
\item
  Edward Greig (GitHub \texttt{Metallicow}): Artwork, Bug Fixes
\item
  Sonia Entzinger: Translation
\item
  SushiTee (GitHub \texttt{SushiTee}): Bug Fixes
\item
  Vathonie Lufh (GitHub \texttt{x2nie}): Bug Fixes, Bindings
\item
  Nina Paley: Designs
\item
  Theodore Gray: Designs
\item
  Jens-Wolfhard Schicke-Uffmann (GitHub \texttt{Drahflow}): Bug Fixes
\item
  Robin Swift: (GitHub \texttt{robin-swift}) Core Developer,
  Documentation
\end{itemize}
