\section{House Style}

These are rules for the general intended style of Embroidermodder's GUI source
code. Not included are anything that a compiler will warn you about: fixing
compiler warnings is more important than fixing style.

Most of this section is rationale, so skip to the end for the summary.

NEW DEVELOPERS: if your patch to Embroidermodder doesn't follow these rules,
don't worry about it. We only ask that your source code follow the basic rules
in the developer training section. These rules are for sculpting Embroidermodder
into a body of code that is resiliant to future bugs and reliable for users.

\subsection{Brevity}

Readable source code is short. Developers have finite time and becoming
acquainted with more than 1000 lines of dense C code is often too high a bar
for a new developer to a project. However, this leads to a bunch of tradeoffs
that have caused issues, so instead we consider the "minimal library"
rather than "minimal code" approach. Not everyone will have used the more
abstract, syntactic features of C++ like templates and operator overloading.
Even if they are capable developers with these features it makes debugging far
harder since the choice of called function is interpreted by the compiler and compiler
errors are hundred line monsters per infraction of "these are all of the possible
variations of this function that don't match".

Using C++'s `unordered_map` can simplify source code in that anything can
map to anything. However, it also means we don't have to associate related structures.
For example the `action_table` came together replacing a collection of unordered maps
with one, then replaced the mapping with labelled indices. Since the `actuator_core`
is a giant switch/case statement this cuts the step of identifying the action by its
label `std::string`.
The structure given by this table allowed the code to be much
easier to interpret. So for this reason we don't recommend the use unordered maps or hashes any more.

\subsection{Rigidity Vs. Ease of Modification}

Difficult to restructure code is good if the structure that's there is good.
It guides new developers into safe practices without having to explain them.
Therefore we want ease of modification that comes from well chosen `structs`
and a carefully curated global header of .

\subsection{Developer Prose}


\subsection{Macro Policy}

Macros are great, you can do all sorts with them. But it's easy to make readable
short code that is really difficult to safely modify.

\subsection{Function Style}

\begin{enumerate}
\item Don't write a new convenience function unless there are two
existing applications of it in the source code.
\item 
\end{enumerate}

\subsection{Summary}

\begin{itemize}
\item 
\end{itemize}

